Forecasting Gamma-Ray Bursts using Gravitational Waves

### 2018-11-22 Paper/Manuscript.tex
Minor
Minor updates

For Einstein Telescope, we consider both $\bar{\rho}_\text{tot}=12$ and 20 given its low-frequency sensitivity. We present the resulting advance warning times ($T_\text{AW}$) in Table~\ref{table:SNR_12_20_results}
on the next page. Comparing these with the corresponding ones in Table~\ref{table:ET}, we see that setting
$\bar{\rho}_\text{tot}=12$ increases ET-B, C warning times by $\gtrsim 50\%, \sim 20\%$, respectively.
On the other hand, $\bar{\rho}_\text{tot}=20$ decreases them by $\sim 40\%, 20\%$.
Be that as it may, we see that ET-C sensitivity still yields advance warning times $> 1\,$hour for sources within $\approx 450$\,Mpc. Therefore, our conclusions that we expect ET-C to forecast $\gtrsim 5$ yearly
BNS mergers holds.

@@

The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals.

@@

Therefore, erring on the side of optimism, we conclude that the 2030s hold in store real-time 
electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.}.

>>>>

For Einstein Telescope, we consider both $\bar{\rho}_\text{tot}=12$ and 20 given its low-frequency sensitivity. We present the resulting advance warning times ($T_\text{AW}$) in Table~\ref{table:SNR_12_20_results}
on the next page. Comparing these with the corresponding ones in Table~\ref{table:ET}, we see that setting
$\bar{\rho}_\text{tot}=12$ increases ET-B, C warning times by $\gtrsim 50\%, \sim 20\%$, respectively.
On the other hand, $\bar{\rho}_\text{tot}=20$ decreases them by $\sim 40\%, 20\%$.
Be that as it may, we see that ET-C sensitivity still yields advance warning times $> 1\,$hour for sources within $\approx 450$\,Mpc. Therefore, our conclusions that we expect ET-C to forecast $\sim \ord(100)$ yearly
BNS mergers holds.

@@

The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals. The light red curve shows the L1 ASD during GW170817.

@@

Therefore, erring on the side of optimism, we conclude that the 2030s\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.} 
hold in store 
(i) forecasts of $\gtrsim \ord(100)$ short gamma-ray bursts and
(ii) real-time electromagnetic observations of $\gtrsim \ord(10)$ of these and the subsequent kilonovae.
